---
title: "Codebook"
output: html_document
author: Calli Beck (calli_beck@clarke.edu)
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Total Income 2021

## Description

Selected Characteristics of People 15 Years Old and Over by Total Money Income in 2021, Work Experience in 2021, Race, Hispanic Origin, and Sex

## Format

#### Characteristics:

15 years and older

Under 65 Years

15 to 24 years

25 to 34 years

25 to 29 years

30 to 34 years

35 to 44 years

35 to 39 years

40 to 44 years

45 to 54 years

45 to 49 years

50 to 54 years

55 to 64 years

55 to 59 years

60 to 64 years

65 years and over

65 to 74 years

65 to 69 years

70 to 74 years

75 years and over

Mean Age

Rows 3 through 22 describe different age ranges recording the number of people based on their income level

Row 23 describes the mean age and how many are at each income level

## Details

This table shows how many people exist in different income levels based on different age ranges.

## Purpose

The purpose of this table is to highlight the amount of people in poverty and what age range is affected the most.

## Overview

This tables shows that while we would expect the amount of people income to be higher in age, there are more younger people receiving higher income than the other way around. It shows how poverty not only affects young people, but it also affects older people as well. The middle ground (40 to 54 years) actually have the most people in higher income levels.

## Source

United States Census Bureau

```{r}

```
